Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)\\ Technical Appendix Including Proofs and Details

### 2017-09-07 fully-abstract-comp/technical-report.tex
another comment

To remedy this, we decided to modify our source language to use a different way of interacting with the stack.
This alternative approach stays even closer to the target language.
Specifically, rather than using push/pop and call/return instructions, we do not add any instructions, but instead use special token values that play the role of the stack pointer/return pointer.
Specifically, as shown in \cref{sec:domains}, there are new token capabilities $\stkptr{\permbnf,\basebnf,\aendbnf,\addrbnf}$, $\retptrd$ and $\retptrc$ which represent a copy of the stack pointer, and the code and data parts of the sealed return closure.
Rather than invoking push or pop, one would store into the $\stkptr{}$ and modify its current address and as we can see in \cref{sec:source-language}, this has the semantic effect that one would expect.
Similarly, rather than invoking return, one would ccall the $\retptrd$ and $\retptrc$ sealed code/data pair.
Finally, rather than invoking call, \dominique{7-9-2017: err, what's the reason we don't follow the same pattern for call?}.
\lau{07-09-2017: One would use $\scall{}{}$ with a pair of sealed capabilities to securely jump to this pair - that is to have this pair executed in a new stack frame. The return would happen just by using $\sxjmp{}{}$ with the $\retptrd$ and $\retptrc$. However, this would work with the local capabilities as the real implementation of $\retptrd$ would be a sealed version of the entire stack pointer. In other words, upon jumping back no extra work would have to be done. Now, however, the old stack pointer should be spliced (using the new $\ssplice{}{}$ instruction) with the stack pointer we sent away in order to regain the old stack pointer. In other words, we need something to recognise when a return happens.}

>>>>

To remedy this, we decided to modify our source language to use a different way of interacting with the stack.
This alternative approach stays even closer to the target language.
Specifically, rather than using push/pop and call/return instructions, we do not add any instructions, but instead use special token values that play the role of the stack pointer/return pointer.
Specifically, as shown in \cref{sec:domains}, there are new token capabilities $\stkptr{\permbnf,\basebnf,\aendbnf,\addrbnf}$, $\retptrd$ and $\retptrc$ which represent a copy of the stack pointer, and the code and data parts of the sealed return closure.
Rather than invoking push or pop, one would store into the $\stkptr{}$ and modify its current address and as we can see in \cref{sec:source-language}, this has the semantic effect that one would expect.
Similarly, rather than invoking return, one would ccall the $\retptrd$ and $\retptrc$ sealed code/data pair.
Finally, rather than invoking call, \dominique{7-9-2017: err, what's the reason we don't follow the same pattern for call?}.
\lau{07-09-2017: One would use $\scall{}{}$ with a pair of sealed capabilities to securely jump to this pair - that is to have this pair executed in a new stack frame. The return would happen just by using $\sxjmp{}{}$ with the $\retptrd$ and $\retptrc$. However, this would work with the local capabilities as the real implementation of $\retptrd$ would be a sealed version of the entire stack pointer. In other words, upon jumping back no extra work would have to be done. Now, however, the old stack pointer should be spliced (using the new $\ssplice{}{}$ instruction) with the stack pointer we sent away in order to regain the old stack pointer. In other words, we need something to recognise when a return happens.}
\lau{07-09-2017: On second thought, when compiled all the code necessary for the call will be generated based on the $\scall{}{}$ instruction. The real implementation of the $\retptrc$ will simply point to a piece of clean up code that splices together the old/private stack pointer with the one we got from the untrusted party. This may, however, give some issues when we want to reason about it because there will be a disconnect between where the clean up job is done in the operational semantics of the source language (namely as part of the $\sxjmp{}{}$), but in a translated program, the code that does the clean up origins with the $\scall{}{}$ instruction. }
